Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
Shift crqa package citation

To perform CRQA, the time series must be converted to the same
scale, while still preserving a sampling rate that respects the native
timescale of the system
[cf. Nyquist frequency in signal processing; @grenander1959probability].
Because the social cohesion and event data have different scales and values,
we converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles
(e.g., Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of different
levels of social cohesion and counts of all, positive, and negative events
on each day.

@@

### Windowed Cross-Recurrence Quantification Analysis
We used windowed cross-recurrence quantification analysis
[WCRQA; @webber2005recurrence] to further investigate the evolution of the
temporal dynamics of social cohesion and real-world events. In this analysis,
a smaller “window” of time points is used to calculate CRQA and capture more
fine-grained dynamics of two time series. The window remains the same size and
“slides” diagonally up the line of identity. The changes in the CRQA metrics
across the windows can reveal changes in dynamics that can then be linked to
external, real-world events.

@@

## Cross-Recurrence Quantification Analysis
CRQA was performed using the `crqa` package [@R-crqa] for R [@R-base]. We 
conducted a permutation test to check for statistical difference from chance 
for all analyses and metrics.

>>>>

To perform CRQA, the time series must be converted to the same
scale, while still preserving a sampling rate that respects the native
timescale of the system
[cf. Nyquist frequency in signal processing; @grenander1959probability].
Because the social cohesion and event data have different scales and values,
we converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles
(e.g., Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of different
levels of social cohesion and counts of all, positive, and negative events
on each day. 
We implemented CRQA using the `crqa` package [@R-crqa] for R [@R-base].

@@

### Windowed Cross-Recurrence Quantification Analysis
We used windowed cross-recurrence quantification analysis
[WCRQA; @webber2005recurrence] to further investigate the evolution of the
temporal dynamics of social cohesion and real-world events. In this analysis,
a smaller “window” of time points is used to calculate CRQA and capture more
fine-grained dynamics of two time series. The window remains the same size and
“slides” diagonally up the line of identity. The changes in the CRQA metrics
across the windows can reveal changes in dynamics that can then be linked to
external, real-world events. 
We implemented WCRQA using the `crqa` package [@R-crqa] for R [@R-base].

@@

## Cross-Recurrence Quantification Analysis
